Bike Share Chronicles_Unveiling Patterns

### 2023-10-24 uci-bike-sharing-dataset/Paper_Summary.rmd
Update Paper_Summary.rmd

**What Are the Year-wise Distribution Patterns of Casual and Registered Bike Sharing Users?**
```{r}
# Create a pie chart for Year 0
labels <- c(
  paste("Casual: ", scales::percent(yearly_totals$Casual_Percentage / 100), sep = ""),
  paste("Registered: ", scales::percent(yearly_totals$Registered_Percentage / 100), sep = "")
)
pie(c(yearly_totals$Casual_Percentage, yearly_totals$Registered_Percentage), labels = labels, col = pie_colors, main = "Year 0: Casual and Registered Users")

>>>>

**What Are the Year-wise Distribution Patterns of Casual and Registered Bike Sharing Users?**
```{r}
filtered_data <- bike_df %>% filter(Year == 0)
filtered_data1 <- bike_df %>% filter(Year == 1)
# Calculate the total Casual and Registered counts for the filtered data
yearly_totals <- filtered_data %>%
  group_by(Year) %>%
  summarize(Casual_Total = sum(Casual), Registered_Total = sum(Registered))
yearly_totals1 <- filtered_data1 %>%
  group_by(Year) %>%
  summarize(Casual_Total1 = sum(Casual), Registered_Total1 = sum(Registered))
# Calculate the percentages for Casual and Registered users
yearly_totals$Casual_Percentage <- (yearly_totals$Casual_Total / (yearly_totals$Casual_Total + yearly_totals$Registered_Total)) * 100
yearly_totals$Registered_Percentage <- (yearly_totals$Registered_Total / (yearly_totals$Casual_Total + yearly_totals$Registered_Total)) * 100
yearly_totals1$Casual_Percentage1 <- (yearly_totals1$Casual_Total1 / (yearly_totals1$Casual_Total1 + yearly_totals1$Registered_Total1)) * 100
yearly_totals1$Registered_Percentage1 <- (yearly_totals1$Registered_Total1 / (yearly_totals1$Casual_Total1 + yearly_totals1$Registered_Total1)) * 100
# Colors for the pie chart slices
pie_colors <- c("lightblue", "lightgreen")
# Create a pie chart for Year 0
labels <- c(
  paste("Casual: ", scales::percent(yearly_totals$Casual_Percentage / 100), sep = ""),
  paste("Registered: ", scales::percent(yearly_totals$Registered_Percentage / 100), sep = "")
)
pie(c(yearly_totals$Casual_Percentage, yearly_totals$Registered_Percentage), labels = labels, col = pie_colors, main = "Year 0: Casual and Registered Users")
